Fourmile Calibrations and Output

### 2023-05-02 38HRU_model/fourmile_model_outputs.Rmd
updates
NEED TO RERUN CALS!
adding burn stuff

@@

#name all the csv
names(dataframes) <- substr(filenames, 1, 9)

@@

grid_2011 <- read_cals(grid2011., name = 'grid_2011')
grid_2012 <- read_cals(grid2012., name = 'grid_2012')
grid_2013 <- read_cals(grid2013., name = 'grid_2013')
grid_2014 <- read_cals(grid2014., name = 'grid_2014')
grid_2015 <- read_cals(grid2015., name = 'grid_2015')
grid_2016 <- read_cals(grid2016., name = 'grid_2016')
grid_2017 <- read_cals(grid2017., name = 'grid_2017')
grid_2018 <- read_cals(grid2018., name = 'grid_2018')
grid_2019 <- read_cals(grid2019., name = 'grid_2019')
grid_2020 <- read_cals(grid2020., name = 'grid_2020')
grid_all <- read_cals(gridall.c, name = 'grid_all')

@@

statn_2011 <- read_cals(statn2011, name = 'statn_2011')
statn_2012 <- read_cals(statn2012, name = 'statn_2012')
statn_2013 <- read_cals(statn2013, name = 'statn_2013')
statn_2014 <- read_cals(statn2014, name = 'statn_2014')
statn_2015 <- read_cals(statn2015, name = 'statn_2015')
statn_2016 <- read_cals(statn2016, name = 'statn_2016')
statn_2017 <- read_cals(statn2017, name = 'statn_2017')
statn_2018 <- read_cals(statn2018, name = 'statn_2018')
statn_2019 <- read_cals(statn2019, name = 'statn_2019')
statn_2020 <- read_cals(statn2020, name = 'statn_2020')
statn_all <- read_cals(statnall., name = 'statn_all')

@@

>>>>

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model')

@@

#name all the csv
names(dataframes) <- substr(filenames, 1, 10)

@@

grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
grid_all <- read_cals(grid_all.c, name = 'grid_all')

@@

statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
statn_all <- read_cals(statn_all., name = 'statn_all')

@@

## Burn params

```{echo = FALSE, message = FALSE, warning = FALSE, include = F}

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=TRUE)

#name all the csv
names(dataframes) <- substr(filenames, 1, 10)

# read in all the grid burn params
read_cals_burn <- function(df, name){
    df <- df %>%
      slice(-c(1:274)) %>%
      separate_wider_delim(Parameter, 
                       delim = ',',
                       names = c('soilID',
                                 'luca_a_rain',
                                 'luca_a_snow',
                                 'luca_soilMaxInfSummer',
                                 'luca_soilMaxDPS',
                                 'luca_lagSurfaceRunoff',
                                 'luca_soilDistMPSLPS')) %>%
      slice(-1) %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)
}

grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')

grid_burn <- bind_rows(grid_2011_burn, 
                  grid_2012_burn, 
                  grid_2013_burn, 
                  grid_2014_burn, 
                  grid_2015_burn,
                  grid_2016_burn, 
                  grid_2017_burn, 
                  grid_2018_burn, 
                  grid_2019_burn, 
                  grid_2020_burn,
                  grid_all_burn) %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

# now do statn burn params
statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')

statn_burn <- bind_rows(statn_2011_burn, 
                  statn_2012_burn, 
                  statn_2013_burn, 
                  statn_2014_burn, 
                  statn_2015_burn,
                  statn_2016_burn, 
                  statn_2017_burn, 
                  statn_2018_burn, 
                  statn_2019_burn, 
                  statn_2020_burn,
                  statn_all_burn) %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

burn_params <- bind_rows(grid_burn, statn_burn) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  summarise(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  pivot_longer(!cal, 
               names_to = 'params',
               values_to = 'value')

```{r}

# plot_burnparams <- function(param_name) {
#   params %>%
#     filter(params == param_name) %>%
#     ggplot(aes(x = value,
#                y = cal)) + 
#     geom_point() +
#     ggtitle(param_name) +
#     theme_bw()
# }
# 
# name <- levels(burn_params$params)
# 
# lapply(name, plot_burnparams)
